%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV for A4 paper format
% XeLaTeX Template
% Version 1.1
%
% A4 version author:
% Marvin Frommhold (depressiverobot.com)
% https://github.com/depressiveRobot/friggeri-cv-a4
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Options
% 'print': remove colors from this template for printing
% 'nocolors' to disable colors in section headers
\documentclass[]{friggeri-cv-a4}

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Kimmo}{Ahokas}{Cloud Engineer}

%----------------------------------------------------------------------------------------
% SIDEBAR SECTION
%----------------------------------------------------------------------------------------

% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    Naulakalliontie 23~B~7
    00970 Helsinki
    Finland
    +358 50 533 1351
    ~
    \href{mailto:kimmo.ahokas@gmail.com}{kimmo.ahokas@gmail.com}
    \href{http://kimia.fi}{http://kimia.fi}
    \href{https://github.com/kimmoahokas}{GitHub}
    \href{https://www.linkedin.com/in/kimmoahokas}{LinkedIn}
    \href{https://twitter.com/kimmoahokas}{Twitter}
  \section{languages}
    Native Finnish
    Excellent English
    Basic Swedish
  \section{programming}
    Python, TypeScript
    HTML, JS, CSS
    Java, Scala
  \section{technology}
    Linux
    AWS
    Docker
    Networking
\end{aside}

\section{education}

\begin{entrylist}
  \entry
    {2014 - 2016}
    {Master of Science (Technology)}
    {Aalto University}
    {Major: Data Communications Software\\
    Master's Thesis: "Load balancing in LTE core network with OpenStack clouds:
    Design and implementation"\\
    Grade: 3.86}
  \entry
    {2009 - 2014}
    {Bachelor of Science}
    {Aalto University}
    {Major: Data Communications Software\\
    Minor: Software Technology\\
    Bachelor's Thesis: "Mobiilien tietoliikennejärjestelmien emulointi"\\
    Grade: 3.36}
  \entry
    {2005 - 2008}
    {Undergraduate}
    {Savonlinna lyceum upper secondary school}
    {Grades: Mathematics, Physics, English: Eximia cum laude approbatur; Native Language: Magna cum laude approbatur; Swedish: Cum laude approbatur}
\end{entrylist}

\section{experience}

\begin{entrylist}
    \entry
    {2020 - }
    {Futurice Oy}
    {DevOps specialist}
    {\emph{Working on a client project with B2B eCommerce solution, data lake and online licensing system. Full end-to-end experience from planning to implementation and daily operation of the systems using ECS, EKS, Api Gateway, Lambda and many more services.}}
  \entry
    {2015 - 2020}
    {Futurice Oy}
    {IT specialist}
    {\emph{Jack of all trades in internal IT team. Planning and maintaining networks, migrating workloads from physical hardware to AWS, supplier management and user support.}}
  \entry
    {2012 - 2015}
    {Aalto University}
    {Research Assistant / Course Assistant}
    {\emph{Assisting on courses "T-110.2100 Introduction to Datacommunications", "T-110.4100 Computer Networks", "T-110.5102 Laboratory Works in Networking and Security" and "T-110.5130 Mobile Systems Programming". Research related to the topics of my Master's and Bachelor's topics.}}
  \entry
    {05 – 08 2011}
    {Nokia Siemens Networks}
    {Seasonal trainee}
    {\emph{Maintaining, improving and developing software deployment framework for Linux based IP networking platform. Basically this was Bash and Python scripting.}}
\end{entrylist}

\section{Certifications}
  \begin{entrylist}
    \entry
      {20.1.2020}
      {AWS Certified Solutions Architect - Associate}
      {}
      {\href{https://www.credly.com/badges/1a48ceb8-1156-43b3-9385-4eaaa55743fc/linked_in_profile}{Verification Link}}
  \end{entrylist}

\section{positions of responsibility}
  \begin{entrylist}
    \entry
      {01-12 2013}
      {Tietokilta ry}
      {Member of the board}
      {\emph{Responsibility area: Study politics}}
  \end{entrylist}

\end{document}
